{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-01-29 documents/acknowledgement.tex
gosh darnit

@@

@@

Chengxiang Li and the team of who appear to have spent a decade iterating the Marx avalanche generator we use in this paper. It is an excellent, very high performance design.

>>>>

Conflicts of interest

Funded in part by the author's company, SafeSump Inc., and Ideal Consulting Inc., whatever that's worth.

@@

Sci-Hub

@@

Chengxiang Li and the team of who appear to have spent a half-decade iterating the Marx avalanche generator we use in this paper. It is an excellent, very high performance design.

### 2021-01-29 documents/charge.tex
gosh darnit

The adsorption of metal ions onto the surface of the genome
\begin{itemize}
\item The nucleocapsid. 
\item Induced polarization
		Persson cite a re-arrangement of electrons as a source of drag. Polarization-like effects are not expected. We have not followed up on this.

\item 
\end{itemize}

@@

@@

@@

@@

\begin{sidenote}
Protein net charges extracted from protein primary structure sequences\footnotemark compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt\footnotemark using localCIDER \cite{CIDER2017}. See \ghfile{biology/data/net_charge.py} and structure.xlsx. Detailed source information will be added later!
\end{sidenote}
Assuming a charge of $2e^-$ per base pair due to phosphate groups, the 13.5 kbp of RNA can hardly contribute $> 3e^- \times10^4$

>>>>

The adsorption of metal ions onto the surface of the genome
\begin{itemize}
\item The nucleocapsid. 
\item Induced polarization
		Persson cite a polarization re-arrangement of electrons as a source of drag. Polarization-like effects are not expected. We have not followed up on this.
\item 
\end{itemize}

\section{Weakened phage}

should try weakened phage again!

Poisson-Boltzmann family of equations is an extension of standard Laplace and Poisson potentials to solutions containing ions. As with all models, there are many nuances to using these correctly; whether various approximations hold, etc. We will ignore all subtleties.

The generalized Poisson equation is

$$\nabla \cdot \left(\epsilon\ \nabla \bar\phi \right) = - \rho$$

We shamelessly steal Brackley \cite{Electrostatic2020}'s formulation (thanks for such detail!)  with one exception. Most solutions consider an equilibrium. However, we are specifically designing the pulse to be too short for ion equilibriation to occur. Therefore we solve in two steps: First the Poisson-Boltzmann equation is run to determine the charge density due to screening; then this is used as a constant to solve when a field is applied.

Reproducing here for convenience:

$$\nabla \cdot \left(\epsilon\ \nabla \bar\phi \right) - \epsilon \kappa^2 \sinh(\bar\phi) = - \rho$$

is the potential in V, kappa is a Debye-Huckel parameter. They use an internal dielectric constant of 5, an external of 80 ($\epsilon =  80\epsilon_0$). 1/10 k1

$$\hat\phi = \frac{e_0 \phi}{}$$

where $e_0$ is the electron charge, $k_b$ the Boltzmann constant, and

@@

\subsection{Empirical methods}

@@

electroroattion

@@

(29.8 kb to 29.9 kbp for NCoV-2 \cite{Genomic2020}).

@@

\begin{sidenote}
Protein net charges extracted from protein primary structure sequences\footnotemark compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt\footnotemark using localCIDER \cite{CIDER2017}. See \ghfile{biology/data/net_charge.py} and structure.xlsx. Detailed source information will be added later!
\end{sidenote}

NOTE SSRNA Assuming a charge of $1e^-$ per base pair due to phosphate groups, the 13.5 kbp of ssRNA can hardly contribute $> 1.5e^- \times10^4$

### 2021-01-29 documents/detection.tex
Writing notes
Writing, re-organizing references
gosh darnit

\begin{autem}
	I hasten to note that quantifying viral titer is a completely solved problem, and is a procedure often done in kindergarten labs. The amount of time and effort we spent here was completely unjustifiable. It was driven by an acute lack of competence, equipment, and the small volume constraints of our original poorly designed microwave setup.
\end{autem}

@@

\subsubsection{Detect the release of intracellular material due to the lysis of the host}

@@

\subsubsection{Detect the lysis of the virus, and the release of intra-viral material}

@@

\subsubsection{Directly detect the virus itself}

>>>>

\begin{autem}
	I hasten to note that quantifying viral titer is a completely solved problem, and is a procedure often done in kindergarten labs. The amount of time and effort we spent here was completely unjustifiable. It was driven by an acute lack of competence, equipment, and the 0.8 uL volume constraints of our original poorly designed microwave setup.
\end{autem}

@@

\subsection{Detect the release of intracellular material due to the lysis of the host}

@@

\subsection{Detect the lysis of the virus, and the release of intra-viral material}

@@

\subsection{Directly detect the virus itself}
